\begin{frame}
\section{}
You know LDA/Fisher. Consider a two class problem with two samples $((2,3),+)$ and $((3,4),-)$. $S_w$ is regularized as
$S_w + \sigma I$. The LDA solution ${\bf w}^*$ will be:
\begin{enumerate}[label=(\Alph*)]
\item along the direction of $(2,3)$ and $(3,4)$     % Ans
\item orthogonal to the direction of $(2,3)$ and $(3,4)$
\item neither along nor orthogonal to
the direction of $(2,3)$ and $(3,4)$.
\item If we have not regularized, $S_w$ would have become a NULL matrix.     % Ans
\item None of the above.  % None
\end{enumerate}
\end{frame}

\begin{frame}
\section{}
You know LDA/Fisher. The goal is to:

\begin{enumerate}[label=(\Alph*)]
\item maximize inter class scatter    % Ans
\item minimize inter class scatter
\item maximize within class scatter
\item minimize within class scatter   % Ans
\item Any two of the above.  % None
\end{enumerate}
\end{frame}

\begin{frame}
\section{}
You know LDA/Fisher.
There are two classes $\omega_1$ and $\omega_2$. $d=4$. Both are multivariate Gaussians with $\Sigma = I$. There are 50 and 100 samples from these two classes respectively. i.e., $N=150$.
The rank of $S_B$ is
\begin{enumerate}[label=(\Alph*)]
\item 1   % Ans
\item 2
\item 150(N)
\item 4 (d)
\item None of the above   % None
\end{enumerate}
\end{frame}


\begin{frame}
\section{}
You know LDA/Fisher. There are two classes $\omega_1$ and $\omega_2$. $d=4$. Both are multivariate Gaussians with $\Sigma = I$. There are 50 and 100 samples from these two classes respectively. i.e., $N=150$.

What is the rank of $S_w$ is:
\begin{enumerate}[label=(\Alph*)]
\item 2
\item 4   % Ans
\item 1
\item 100
\item 150
\end{enumerate}
\end{frame}

\begin{frame}
\section{}
You know LDA/Fisher for two class classification problem. We know the problem as solving for:

\[ S_b u = \lambda S_w u\] and the  solution as:

\[ u^* = \alpha S_w^{-1} [\mu_1 - \mu_2] \]

\begin{enumerate}[label=(\Alph*)]
\item Both $S_B$ and $S_w$ are of $d\times d$.     % Ans
\item Given the problem statement, we can write $S_b  = \lambda S_w$. Or one matrix is the scaled version of the other.
\item There is one and only one $u$ that satisfy the problem. (or solution to the problem is unique).
\item $u^*$ is obtained by solving our problem with an additional constraint of $||u||_2^2 =1$
\item None of the above.    % None
\end{enumerate}
\end{frame}
