\begin{frame}
\section{}
A Fully connected layer has 100 neurons at
input and 100 neurons at output. The number of parameters to learn is:

(Assume there is no bias.)
\begin{enumerate}[label=(\Alph*)]
\item 1000
\item 10000   % Ans
\item 200
\item 50
\item None of the above  % None
\end{enumerate}
\end{frame}

\begin{frame}
\section{}
A convolutional layer has 100 inputs and
100 outputs there is sufficient zero padding. The
number of learnable parameters is:

\begin{enumerate}[label=(\Alph*)]
\item 10
\item 3
\item 5
\item 1
\item Any of the above   % Ans  % None
\end{enumerate}
\end{frame}

\begin{frame}
\section{}
A convolutional layer has 100 inputs and
5 channels of 100 outputs there with sufficient
zero padding. The number of learnable parameters is:
Each output channel is computed with 7 learnable weights.

Total number of learnable parameters is:

\begin{enumerate}[label=(\Alph*)]
\item 7
\item 5
\item 12
\item 35    % Ans
\item None of the above  % None
\end{enumerate}
\end{frame}


\begin{frame}
\section{}
A convolution layer has 3 input channels of size 100 each. Output is computed over a 1-D window of length 5. There are 7 output channels. Stride is 2.

How many learnable parameters exist in this layer?
% FIB
\end{frame}

\begin{frame}
\section{}
We know that if there is no zero padding, the convolution output is smaller than the original. Consider an input of size/length 100. Convolution is carried over a window of length 7 with stride of 1. What is the length/size of output?
% FIB
\end{frame}
