
\begin{frame}
\section{}
In  a MCQ a student randomly guesses from the options if she does not know. Given that there were $[m]$ choices in a question and that $[p]$ is the chance she knows the answer, what is the probability that she knew the answer if she answered correctly?
\begin{enumerate}
\item $ \frac {[m*p]} {[1+m*p]} $
\item $ \frac {1} {[1+(m-1)*p]} $
\item $ \frac {1} {[1+m*p]} $
\item $ \frac {[m*p]} {[1+(m-1)*p]} $   % Ans
\end{enumerate}
%Ans: D
\end{frame}

\begin{frame}
\section{}
Bag I contain $[w_1]$ white and $[b_1]$ black balls. Bag II contains $[w_2]$ white and $[b_2]$ black balls.

A ball is drawn at random from one of the bags, and it is found to be white. What is the probability that it was drawn from Bag I.
\begin{enumerate}
\item $\frac{[w_1]}{[w_1 + b_1]}$
\item $\frac{[w_1*(w_1+b_1)]}{[w_1*(w_1+b_1) + w_2*(w_2+b_2)]}$
\item $\frac{[w_1*(b_1+b_2)]}{[w_1*(b_1+b_2) + w_2*(b_1+b_2)]}$
\item $\frac{[w_1*(w_2+b_2)]}{[w_1*(w_2+b_2) + w_2*(w_1+b_1)]}$    % Ans
\end{enumerate}
% Ans: D
\end{frame}

\begin{frame}
\section{}
A man is known to speak truth $[K]$ out of 10 times. He throws a die and reports that number obtained is a four. Find the probability that the number obtained is actually a four.
\begin{enumerate}
\item $\frac 1 6$
\item $\frac {[K]}{[60-5*K]} $
\item $\frac {[K]}{[40-3*K]} $
\item $\frac {[K]}{[50-4*K]} $   % Ans
\end{enumerate}
% Ans: D
\end{frame}

\begin{frame}
\section{}
Given the following confusion matrix what is the precision?
\begin{table}[!htbp]\centering\begin{tabular}{|c|c|c|}
\hline
& Predicted +ve & Predicted -ve \\ \hline
Actual +ve & [A]            & [B]             \\ \hline
Actual -ve & [C]             & [D]             \\ \hline
\end{tabular}\end{table}
\begin{enumerate}
\item $\frac{[A]}{[A+B]}$
\item $\frac{[A]}{[A+C]}$   % Ans
\item $\frac{[A+D]}{[A+B+C+D]}$
\item $\frac{[D]}{[D+C]}$
\end{enumerate}
% Ans: B
\end{frame}

\begin{frame}
\section{}
Consider that numbers from 1 to $[N**2]$ are arranged in a $[N]$ by $[N]$ dimensional square matrix $M$ in a way such that first $[N]$ numbers are in row 1, next $[N]$ numbers in row 2 and so on. The rank of $M$ is
\begin{enumerate}
\item 1
\item 2   % Ans
\item $[N]$
\item None of these
\end{enumerate}
% Ans: B
\end{frame}
